---
title: "Cluster_Profiler_Hallmarks"
output: html_document
date: "2022-11-07"
---
#Details: 
### This is to do a GSEA analysis using ONLY the MsigDB Hallmark pathways 
### This is not done with clusterprofiler that I could find 
### Clusterprofiler uses the Biological processes, molecular funtion, and cellular component options 
### Generally speaking, what we want appears to be more niche than the base GSEA options 
### So the next option is to find something that incorporates the MsigDB hallmark option 
#### What I have found is the CRAN package msigdbr and I am going to attempt that and see what happens 
#### I have checked for incorporation of msigdbr and clusterprofiler, and there is a sketchy documented way to do it 

##CRAN Project Vignette: 
https://cran.r-project.org/web/packages/msigdbr/vignettes/msigdbr-intro.html

## Options for this analysis (more in depth)
https://yulab-smu.top/biomedical-knowledge-mining-book/semantic-similarity-overview.html 

Perks of the package: 
There are all of them msigdb options present (that I know of) AND multiple species
It is ridiculously basic 
Formats make the tibble function easy to use without extra data wrangling 

Set up (from the Vignette)
```{r echo=FALSE, message= FALSE, warning= FALSE}
library("msigdbr")
library(clusterProfiler)
library(enrichplot)
# we use ggplot2 to add x axis labels (ex: ridgeplot)
library(ggplot2)
library(cowplot)
# SET THE DESIRED ORGANISM HERE
organism = "org.Hs.eg.db"
#BiocManager::install(organism, character.only = TRUE)
library(organism, character.only = TRUE)
```

```{r echo=FALSE, message= FALSE, warning= FALSE}
#to get the gene set that we want
#in this particular setting we want the H genes, which are Hallmark genes 
h_gene_sets = msigdbr(species = "Homo sapiens", category = "H")
```

```{r echo=FALSE, message= FALSE, warning= FALSE}
m_t2g <- msigdbr(species = "Homo sapiens", category = "H") %>% 
  dplyr::select(gs_name, ensembl_gene)
```

#this is from the first go round
```{r echo=FALSE, message= FALSE, warning= FALSE}
# reading in data from deseq2
df = read.csv("~/Downloads/results/all/comparisons/group_P6.6_2D_vs_P0_2D_Wald.csv", header=TRUE)
# we want the log2 fold change 
original_gene_list <- df$log2FoldChange

#list needs no decimal points
no_decimals <- gsub('\\.[0-9]*$','', df$x)
#now we are going to add this to the df 
df$no_decimals <- no_decimals
# name the vector
names(original_gene_list) <- df$no_decimals

# omit any NA values
gene_list<-na.omit(original_gene_list)

# sort the list in decreasing order (required for clusterProfiler)
gene_list = sort(gene_list, decreasing = TRUE)
gene.list <- data.frame(gene_list)
```

```{r echo=FALSE, message= FALSE, warning= FALSE}
em <- enricher(df$no_decimals, TERM2GENE=m_t2g)
```

```{r}
gse <- GSEA(gene_list,  minGSSize = 15, 
             maxGSSize = 500, 
             nPermSimple= 1000,
             pvalueCutoff = 0.05, 
             verbose = TRUE, 
             pAdjustMethod = "none", TERM2GENE= m_t2g)
```
Adjusting for Min, Max, and Permutations to be the same as GSEA software 
Min Size: 15, Max Size 500, Permutations 1000 and no p adj method 

```{r}
require(DOSE)
dotplot(gse, showCategory=10, split=".sign") + facet_grid(.~.sign) + theme(axis.text.y = element_text(size = 4)) 
```

```{r}
require(DOSE)
dotplot(gse, showCategory=20, split=".sign") + facet_grid(.~.sign) + theme(axis.text.y = element_text(size = 4)) 
```

```{r}
gse<-pairwise_termsim(gse, method = "JC", semData = NULL, showCategory = 200)
emapplot(gse, showCategory = 15)  
```

```{r, out.width="50%"}
# categorySize can be either 'pvalue' or 'geneNum'
cnetplot(gse, categorySize="pvalue", foldChange=gene_list, showCategory = 10, node_label= "category", cex_label_category=0.5)
```

```{r}
cnetplot(gse, categorySize="pvalue", foldChange=gene_list, showCategory = 20,  node_label= "category", cex_label_category=0.5)
```

```{r, out.width="50%"}
ridgeplot(gse) + labs(x = "enrichment distribution") + theme(axis.text.y = element_text(size = 5)) 
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P1 <- gseaplot(gse, y = "all", title = gse$Description[1], geneSetID = 1)
P1
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P2 <- gseaplot(gse, by = "all", title = gse$Description[2], geneSetID = 2)
P2
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P3<- gseaplot(gse, by = "all", title = gse$Description[3], geneSetID = 3)
P3
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P4<- gseaplot(gse, by = "all", title = gse$Description[4], geneSetID = 4)
P4
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P5<- gseaplot(gse, by = "all", title = gse$Description[5], geneSetID = 5)
P5
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P6<- gseaplot(gse, by = "all", title = gse$Description[6], geneSetID = 6)
P6
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P7<- gseaplot(gse, by = "all", title = gse$Description[7], geneSetID = 7)
P7
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P8<- gseaplot(gse, by = "all", title = gse$Description[8], geneSetID = 8)
P8
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P9<- gseaplot(gse, by = "all", title = gse$Description[9], geneSetID = 9)
P9
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P10<- gseaplot(gse, by = "all", title = gse$Description[10], geneSetID = 10)
P10
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P11<- gseaplot(gse, by = "all", title = gse$Description[11], geneSetID = 11)
P11
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P12<- gseaplot(gse, by = "all", title = gse$Description[12], geneSetID = 12)
P12
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P13<- gseaplot(gse, by = "all", title = gse$Description[13], geneSetID = 13)
P13
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P14<- gseaplot(gse, by = "all", title = gse$Description[14], geneSetID = 14)
P14
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P15<- gseaplot(gse, by = "all", title = gse$Description[15], geneSetID = 15)
P15
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P16<- gseaplot(gse, by = "all", title = gse$Description[16], geneSetID = 16)
P16
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P17<- gseaplot(gse, by = "all", title = gse$Description[17], geneSetID = 17)
P17
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P18<- gseaplot(gse, by = "all", title = gse$Description[18], geneSetID = 18)
P18
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P19<- gseaplot(gse, by = "all", title = gse$Description[19], geneSetID = 19)
P19
```

```{r}
# Use the `Gene Set` param for the index in the title, and as the value for geneSetId
P20<- gseaplot(gse, by = "all", title = gse$Description[20], geneSetID = 20)
P20
```




