---
title: "Lara Figure"
output: html_document
date: "2023-01-04"
---
#Graphs from Lara with comparisons by group
#they defined up and donw regulation (lfc of 1.5 in this option ) and had the passage comparison.
Need a few things for this to work 
1) On each of the files we are comparing, we need a data column that defines up vs down regulated genes
2) the data of each group 
3) ggplot bar graph for these comparisons 
4) Something on the x axis for what is being compared
5) Make the data make more sense compared to the current figures 

Things I want included in the figure 
ADJUSTED BY THE ADJUSTED P VALUE FIRST. NON SIGNIFICANT P VALS WERE DELETED IN MY NEW FILE 
1) up regulated > LFC 1.5 
2) Down regulated < -1.5 
3) No change as between 1.5 and -1.5 
Bar Graph showing all 3 for each comparison group 
Table showing the percentage of genes in each category 
Files for this are labeled as Comparison Group_Gene_Annotation
Column of interest will be labeled as Group
```{r}
P0_vs_P1 <- read.csv("~/Documents/Mythreye_Lab/anoikis/Mehri_Resha/Gene comparison/P1_vs_P0_Gene_Annotation.csv")
P0_vs_P4 <- read.csv("~/Documents/Mythreye_Lab/anoikis/Mehri_Resha/Gene comparison/P4_vs_P0_Gene_Annotation.csv")
P0_vs_P7 <- read.csv("~/Documents/Mythreye_Lab/anoikis/Mehri_Resha/Gene comparison/P7_vs_P0_Gene_Annotation.csv")
P0_vs_P6 <- read.csv("~/Documents/Mythreye_Lab/anoikis/Mehri_Resha/Gene comparison/P6_vs_P0_Gene_Annotation.csv")
```

```{r}
x <- list(P0_vs_P1= P0_vs_P1,P0_vs_P4= P0_vs_P4,P0_vs_P7= P0_vs_P7, P0_vs_P6= P0_vs_P6)
level_order <- c("No Change", "Down Regulated", "Up Regulated")
#for the actual bar graph itself 
library(ggplot2)
ggplot() +
  geom_bar(data = P0_vs_P1, mapping = aes(x= Group, group =Group, fill = Group), position = "dodge") + xlab("P0 vs P1") + ylab("Total Number of Genes")  
```

```{r}
#for the actual bar graph itself 
ggplot() +
  geom_bar(data = P0_vs_P4, mapping = aes(x= Group, group =Group, fill = Group), position = "dodge") + xlab("P0 vs P4") + ylab("Total Number of Genes") 
```
```{r}
no_decimals <- gsub('\\.[0-9]*$','', P0_vs_P1$gene_id)
#now we are going to add this to the df 
P0_vs_P1$gene_id <- no_decimals
no_decimals <- gsub('\\.[0-9]*$','', P0_vs_P4$gene_id)
#now we are going to add this to the df 
P0_vs_P4$gene_id <- no_decimals
gene_list <- c(P0_vs_P1$gene_id, P0_vs_P4$gene_id, P0_vs_P6$X, P0_vs_P7$x)
```

```{r}
P1 <- P0_vs_P1[ , c(1,6)]
P4 <- P0_vs_P4[ , c(1,6)]
P6 <- P0_vs_P6[ , c(1,4)]
P7 <- P0_vs_P7[ , c(2,7)]
colnames(P1) <- c("gene_id", "P1")
colnames(P4) <- c("gene_id", "P4")
colnames(P6) <- c("gene_id", "P6")
colnames(P7) <- c("gene_id", "P7")
```

```{r}
gene_list_2 <- merge(P1, P4, all.x=TRUE, all= TRUE)
```

```{r}
gene_list_3 <- merge(gene_list_2, P6, all.x=TRUE, all= TRUE)
```

```{r}
gene_list_4 <- merge(gene_list_3, P7, all.x=TRUE, all= TRUE)
```

```{r}
write.csv(gene_list_4, "~/Desktop/genelist.csv")
```

```{r}
#for the actual bar graph itself 
ggplot() +
  geom_bar(data = P0_vs_P7, mapping = aes(x= Group, group =Group, fill = Group), position = "dodge") + xlab("P0 vs P7") + ylab("Total Number of Genes") 
```

I went ahead and manually counted the individual points that are present above so it can be in one graph 
```{r}
library(tidyr)
#read in what we want 
up <- read.csv("~/Desktop/genelist/Up.csv")
down <- read.csv("~/Desktop/genelist/Down.csv")
nc <- read.csv("~/Desktop/genelist/No_Change.csv")
```

#The rest of Lara's figure is made with UpSet Figures 
## Need to use ComplexUpSet because the other one is out of date (yay Lara for telling me)
```{r}
library(ggplot2)
library(ComplexUpset)
```

#THIS WORKED TO MAKE THE RIGHT DATASET. Hopefully 
```{r}
Group <- colnames(up)[c(2:5)]
Group
```

```{r}
upset(up, Group, min_degree=1, sort_sets= FALSE, sort_intersections_by='degree', sort_intersections= "ascending") + ggtitle('Up Regulated Genes') 
```

```{r}
upset(down, Group,  min_degree=1, sort_sets= FALSE, sort_intersections_by='degree', sort_intersections= "ascending") + ggtitle("Down Regulated Genes")
```

```{r}
upset(nc, Group, min_degree=1, sort_sets= FALSE, sort_intersections_by='degree', sort_intersections= "ascending") + ggtitle("Genes with No Significant Change")
```

```{r}
Group <- colnames(up)[c(2, 4:5)]
Group
```

```{r}
upset(up, Group, min_degree=1,sort_sets= FALSE, sort_intersections_by='degree', sort_intersections= "ascending") + ggtitle('Up Regulated Genes') 
```

```{r}
upset(down, Group,  min_degree=1, sort_sets= FALSE, sort_intersections_by='degree', sort_intersections= "ascending") + ggtitle("Down Regulated Genes")
```
```{r}
upset(nc, Group, min_degree=1, sort_sets= FALSE, sort_intersections_by='degree', sort_intersections= "ascending") + ggtitle("Genes with No Significant Change")
```