---
title: "Lara Figure"
output: html_document
date: "2023-01-04"
---
#Graphs from Lara with comparisons by group
#they defined up and donw regulation (lfc of 1.5 in this option ) and had the passage comparison.
Need a few things for this to work 
1) On each of the files we are comparing, we need a data column that defines up vs down regulated genes
2) the data of each group 
3) ggplot bar graph for these comparisons 
4) Something on the x axis for what is being compared
5) Make the data make more sense compared to the current figures 

Things I want included in the figure 
ADJUSTED BY THE ADJUSTED P VALUE FIRST. NON SIGNIFICANT P VALS WERE DELETED IN MY NEW FILE 
1) up regulated > LFC 1.5 
2) Down regulated < -1.5 
3) No change as between 1.5 and -1.5 
Bar Graph showing all 3 for each comparison group 
Table showing the percentage of genes in each category 
Files for this are labeled as Comparison Group_Gene_Annotation
Column of interest will be labeled as Group
```{r}
P0_vs_P1 <- read.csv("~/Documents/Mythreye_Lab/Mehri_Resha/Gene comparison/P1_vs_P0_Gene_Annotation.csv")
P0_vs_P4 <- read.csv("~/Documents/Mythreye_Lab/Mehri_Resha/Gene comparison/P4_vs_P0_Gene_Annotation.csv")
P0_vs_P7 <- read.csv("~/Documents/Mythreye_Lab/Mehri_Resha/Gene comparison/P7_vs_P0_Gene_Annotation.csv")
```

```{r}
x <- list(P0_vs_P1= P0_vs_P1,P0_vs_P4= P0_vs_P4,P0_vs_P7= P0_vs_P7)
level_order <- c("No Change", "Down Regulated", "Up Regulated")
#for the actual bar graph itself 
library(ggplot2)
ggplot() +
  geom_bar(data = P0_vs_P1, mapping = aes(x= Group, group =Group, fill = Group), position = "dodge") + xlab("P0 vs P1") + ylab("Total Number of Genes")  
```

```{r}
#for the actual bar graph itself 
ggplot() +
  geom_bar(data = P0_vs_P4, mapping = aes(x= Group, group =Group, fill = Group), position = "dodge") + xlab("P0 vs P4") + ylab("Total Number of Genes") 
```

```{r}
#for the actual bar graph itself 
ggplot() +
  geom_bar(data = P0_vs_P7, mapping = aes(x= Group, group =Group, fill = Group), position = "dodge") + xlab("P0 vs P7") + ylab("Total Number of Genes") 
```

I went ahead and manually counted the individual points that are present above so it can be in one graph 
```{r}
library(tidyr)
data3 <- read.csv("~/Documents/Mythreye_Lab/Mehri_Resha/Gene comparison/Data_Up_and_Down_Comparisons .csv")
```


```{r}
data5 <- t(data3)
#to edit this data group so only the rows of interest are involved 
data6 <- data5[c(1,3,5,7) , ]
write.csv(data6, "~/Desktop/edits.csv")
```


```{r}
data7 <- read.csv("~/Desktop/edits.csv")
```


```{r}
data8 <- t(data7)
```

#The rest of Lara's figure is made with UpSet Figures 
## Need to use ComplexUpSet because the other one is out of date (yay Lara for telling me)
```{r}
library(ggplot2)
library(tidyr)
library(ComplexUpset)
```

#THIS WORKED TO MAKE THE RIGHT DATASET. Hopefully 
```{r}
Group <- rownames(data6)[c(2:4)]
Group
```


```{r}
upset(data3, Group)
```