---
title: "Lara Figure"
output: html_document
date: "2023-01-04"
---
#Graphs from Lara with comparisons by group
#they defined up and donw regulation (lfc of 1.5 in this option ) and had the passage comparison.
Need a few things for this to work 
1) On each of the files we are comparing, we need a data column that defines up vs down regulated genes
2) the data of each group 
3) ggplot bar graph for these comparisons 
4) Something on the x axis for what is being compared
5) Make the data make more sense compared to the current figures 

Things I want included in the figure 
ADJUSTED BY THE ADJUSTED P VALUE FIRST. NON SIGNIFICANT P VALS WERE DELETED IN MY NEW FILE 
1) up regulated > LFC 1.5 
2) Down regulated < -1.5 
3) No change as between 1.5 and -1.5 
Bar Graph showing all 3 for each comparison group 
Table showing the percentage of genes in each category 
Files for this are labeled as Comparison Group_Gene_Annotation
Column of interest will be labeled as Group
```{r}
P0_vs_P1 <- read.csv("~/Desktop/P1_vs_P0_Gene_Annotation.csv")
P0_vs_P4 <- read.csv("~/Desktop/P4_vs_P0_Gene_Annotation.csv")
P0_vs_P7 <- read.csv("~/Desktop/P7_vs_P0_Gene_Annotation.csv")
```

```{r}
x <- list(P0_vs_P1= P0_vs_P1,P0_vs_P4= P0_vs_P4,P0_vs_P7= P0_vs_P7)
level_order <- c("No Change", "Down Regulated", "Up Regulated")
#for the actual bar graph itself 
library(ggplot2)
ggplot() +
  geom_bar(data = P0_vs_P1, mapping = aes(x= Group, group =Group, fill = Group), position = "dodge") + xlab("P0 vs P1") + ylab("Total Number of Genes")  
```
```{r}
#for the actual bar graph itself 
ggplot() +
  geom_bar(data = P0_vs_P4, mapping = aes(x= Group, group =Group, fill = Group), position = "dodge") + xlab("P0 vs P4") + ylab("Total Number of Genes") 
```
```{r}
#for the actual bar graph itself 
ggplot() +
  geom_bar(data = P0_vs_P7, mapping = aes(x= Group, group =Group, fill = Group), position = "dodge") + xlab("P0 vs P7") + ylab("Total Number of Genes") 
```
I went ahead and manually counted the individual points that are present above so it can be in one graph 
```{r}
library(tidyr)
data3 <- read.csv("~/Desktop/Groups_by_Gene_Count.csv")
data4 <- data[ -1, ]
```


```{r}
data5 <- data4 %>%
  pivot_longer(cols= c(Group.P0_P1, Group.P0_P4, Group.P0_P7), names_to = "time_point", values_to= "counts"
)
```


```{r}
#for the actual bar graph itself 
ggplot() +
  geom_col(data = data2, mapping = aes(x= time_point, group= Group, y= counts, fill= Group), position = "dodge") + xlab("Comparison Groups") + ylab("Total Number of Genes") 
```
#The rest of Lara's figure is made with UpSet Figures 
## Need to use ComplexUpSet because the other one is out of date (yay Lara for telling me)
```{r}
library(ggplot2)
library(tidyr)
library(ComplexUpset)
```

#THIS WORKED TO MAKE THE RIGHT DATASET. Hopefully 
```{r}
data <- as.data.frame(read.csv("~/Desktop/data_table_regulation_comparison_2.csv"))
data2 <- data[ , c(1,2,4,6)]
Group <- colnames(data2)[c(2:4)]
Gene_Change <- colnames(data)[c(3,5,7)]
```

```{r}
upset(data, Group, name='Time Point Comparison', width_ratio=0.1)
```

#Now we have to make this data work to incorporate both pieces of data 
```{r}
data_5 <- data %>%
  pivot_longer(cols= c(Group.P0_P1, Group.P0_P4, Group.P0_P7), names_to = "time_point", values_to= "counts"
)
```


```{r}
upset(data_5, Group, name='Time Point Comparison', base_annotations=list(
        'Intersection size'=intersection_size(
            counts=FALSE,
            mapping=aes(fill=data_5$counts)
        )
    ),
    width_ratio=0.1)
```
#Yay this one worked! Except it held onto the triplicate of when we did pivot_longer 
```{r}
dataP01 <- as.data.frame(paste(data$P0_P1.padj, data$Group.P0_P1))

dataP04 <- as.data.frame(paste(data$P0_P4.padj, data$Group.P0_P4))

dataP07 <- as.data.frame(paste(data$P0_P7.padj, data$Group.P0_P7))

datagene.id <- as.data.frame(paste(data$gene_id))
```


```{r}
write.csv(dataP01, "~/Desktop/P1.csv")
write.csv(dataP04, "~/Desktop/P4.csv")
write.csv(dataP07, "~/Desktop/P7.csv")
write.csv(datagene.id, "~/Desktop/geneid.csv")
```

