---
title: "Treatment15U"
output: html_document
date: "2023-03-23"
---

This is the documentation for the RNAseq tutorial, all in one place. 
First things first, this is meant for you to be able to run with minimal assistance, 
but if you need assistance, let me know. 

Each section of code will have a little play button to run that section individually. 
There is also an option on the top of this screen saying "run" with a green arrow. You 
can run the whole document with the options in that, should you choose. 

Each step will have a lot of documentation as well as where you need to add your own 
information so that it runs correctly. 

For file paths, there will be CHANGE_THIS_PATH/ that you change to match where the files are + the file name 
Other locations will have a CHANGE_THIS and then whatever you need to change 

So here are the steps that need to happen before you use this code: 
- Download the FASTQs onto Cheaha 
- Use Salmon for alignment for count data (this is easiest on Cheaha)
    - Salmon is meant for count data and does NOT give variant data

And this is what is going to happen in this code: 
-   Tximport is a package to import count data from Salmon so that they can be imported into DESeq2
    -   Mike Love's (author for most of the well used RNAseq packages) guide uses either tximport or txmeta
    -   This was done with R and R Studio on my local Mac
-   DESeq2 is the standard publication wise for normalizing counts
    -   This is also Mike Love's package and is crazy well documented 
    -   This was done with R and R Studio on my local Mac
    -   Standard for normalization and analysis in most publications

Now let's do the coding!

This part you will only need to do once to download everything: 

```{r message= FALSE, warning= FALSE, echo=FALSE}
library(tximport)
library(GenomicFeatures)
library(TxDb.Hsapiens.UCSC.hg19.knownGene)
library(DESeq2)
```

The files in this next step can be found in a zip folder on Github called


```{r message= FALSE, warning= FALSE, echo=FALSE}
txdb <- loadDb("C:/Users/empage/Documents/Lab_Stuff/Lab_RNAseq_Tutorial/gencode.v19.annotation.gtf_withproteinids.TxDb")
k <- keys(txdb, keytype = "TXNAME")
tx2gene <- select(txdb, k, "GENEID", "TXNAME")
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
dir <- "C:/Users/empage/Documents/Lab_Stuff/Anoikis/OV90/treatment_15U/quants"  #this is a path that you will change. This is the quants folder from Salmon that should be locally on your computer 
samples <- read.csv(file= "C:/Users/empage/Documents/Lab_Stuff/Anoikis/OV90/treatment_15U/Meta_15U.csv") 
files <- file.path(dir, samples$Sample_ID, "quant.sf")
all(file.exists(files))
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
txi <- tximport(files, type = "salmon", tx2gene= tx2gene, ignoreAfterBar= TRUE)
names(txi)
```


This is for setting up the meta data and DESeq2 object so that you can do your analysis 
```{r message= FALSE, warning= FALSE, echo=FALSE}
sample_meta_data <- read.csv(file= "C:/Users/empage/Documents/Lab_Stuff/Anoikis/OV90/treatment_15U/Meta_15U.csv") 
sampleFiles <- samples$Sample_ID
sampleCondition <- sample_meta_data$Treatment
sampleTable <- data.frame(sampleName = sampleFiles,
                          fileName = sampleFiles,
                          condition = sampleCondition)
sampleTable$condition <- factor(sampleTable$condition)
```


```{r echo=FALSE}
colnames(txi$counts) <- rownames(sampleTable)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- DESeqDataSetFromTximport(txi, sampleTable, ~condition)
dds$group <- factor(sample_meta_data$Passage)
design(dds) <- ~ group
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- DESeq(dds)
```

This is going to tell you information about the results from running DESeq2 
```{r}
res <- results(dds, contrast= c("group", "P0", "P1"))
res
```

This is to save the results so that you can look at them later/ comparisons for analysis 
```{r}
write.csv(res, "CHANGE_THIS_PATH/results_post_vs_pre_aging_tcga.csv")
```


You can set results to whatever you want to compare from the dds object; see documentation for more if you do not like what it auto selects/ you want more than what this did first 
Here is an example template. There's a # in front of it so that it is not running 
```{r}
#res_2 <- results(dds, contrast=c("condition","SAY WHICH ONE","AND THE OTHER"))
```


```{r echo=FALSE}
resOrdered <- res[order(res$pvalue),]
```

Here is another portion to see what all is in the DESeq2 object 
```{r}
summary(res)
```

```{r}
res05 <- results(dds, alpha=0.05)
summary(res05)
```

Now you can start going through the plot functions and seeing what the data actually looks like 
```{r echo=FALSE}
plotMA(res, ylim=c(-2,2))
```

```{r echo=FALSE}
plotMA(res05, ylim=c(-2,2))
```

```{r}
vsd <- vst(dds, blind=FALSE)
```

```{r}
rld <- rlog(dds, blind=FALSE)
```

```{r}
ntd <- normTransform(dds)
```

```{r}
library("vsn")
meanSdPlot(assay(ntd))
```

```{r}
meanSdPlot(assay(vsd))
```

```{r}
sampleDists <- dist(t(assay(vsd)))
```

```{r}
library("RColorBrewer")
library("pheatmap")
sampleDistMatrix <- as.matrix(sampleDists)
rownames(sampleDistMatrix) <- paste(vsd$condition)
colnames(sampleDistMatrix) <- NULL
colors <- colorRampPalette( rev(brewer.pal(9, "Blues")) )(255)
pheatmap(sampleDistMatrix,
         clustering_distance_rows=sampleDists,
         clustering_distance_cols=sampleDists,
         col=colors, annRow= vsd$condition)
```

```{r}
plotPCA(vsd, intgroup=c("condition", "group"))
```

```{r}
plotDispEsts(dds)
```

### Graphs for Genes of Interest
