---
title: "15U_by_Treatment"
output: html_document
date: "2023-06-23"
---
15U 
This is to compare the groups of the anoikis project that have been treated with 15U vs DMSO independent of the passage

```{r message= FALSE, warning= FALSE, echo=FALSE}
library(tximport)
library(GenomicFeatures)
library(TxDb.Hsapiens.UCSC.hg19.knownGene)
library(DESeq2)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
txdb <- loadDb("C:/Users/empage/Documents/Lab_Stuff/Lab_RNAseq_Tutorial/gencode.v19.annotation.gtf_withproteinids.TxDb")
k <- keys(txdb, keytype = "TXNAME")
tx2gene <- select(txdb, k, "GENEID", "TXNAME")
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
dir <- "C:/Users/empage/Documents/Lab_Stuff/Anoikis/OV90/treatment_15U/quants"  #this is a path that you will change. This is the quants folder from Salmon that should be locally on your computer 
samples <- read.csv(file= "C:/Users/empage/Documents/Lab_Stuff/Anoikis/OV90/treatment_15U/Meta_15U.csv") 
files <- file.path(dir, samples$Sample_ID, "quant.sf")
all(file.exists(files))
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
txi <- tximport(files, type = "salmon", tx2gene= tx2gene, ignoreAfterBar= TRUE)
names(txi)
```


This is for setting up the meta data and DESeq2 object so that you can do your analysis 
```{r message= FALSE, warning= FALSE, echo=FALSE}
sample_meta_data <- read.csv(file= "C:/Users/empage/Documents/Lab_Stuff/Anoikis/OV90/treatment_15U/meta_15U_updated.csv") 
sampleFiles <- samples$Sample_ID
sampleCondition <- sample_meta_data$Treatment
sampleTable <- data.frame(sampleName = sampleFiles,
                          fileName = sampleFiles,
                          condition = sampleCondition)
sampleTable$condition <- factor(sampleTable$condition)
```


```{r echo=FALSE}
colnames(txi$counts) <- rownames(sampleTable)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- DESeqDataSetFromTximport(txi, sampleTable, ~condition)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- DESeq(dds)
```


This is going to tell you information about the results from running DESeq2 
```{r}
res <- results(dds, contrast= c("condition", "15U", "DMSO"))
res
```

```{r}
summary(res)
```
```{r}
res05 <- results(dds, alpha=0.05)
summary(res05)
```

Now you can start going through the plot functions and seeing what the data actually looks like 
```{r echo=FALSE}
plotMA(res, ylim=c(-2,2))
```

```{r echo=FALSE}
plotMA(res05, ylim=c(-2,2))
```

```{r}
vsd <- vst(dds, blind=FALSE)
```

```{r}
rld <- rlog(dds, blind=FALSE)
```

```{r}
ntd <- normTransform(dds)
```

```{r}
plotPCA(vsd, intgroup=c("condition"))
```
```{r}
plotDispEsts(dds)
```
