---
title: "Treatment15U"
output: html_document
date: "2023-03-23"
---
15U 
This is to compare the groups of the anoikis project that have been treated with 15U

```{r message= FALSE, warning= FALSE, echo=FALSE}
library(tximport)
library(GenomicFeatures)
library(TxDb.Hsapiens.UCSC.hg19.knownGene)
library(DESeq2)
library(EnhancedVolcano)
library(org.Hs.eg.db)
library(dplyr)
library(tidyr)
```

Option 1: make it with the txdb every time 
```{r message= FALSE, warning= FALSE, echo=FALSE}
#txdb <- loadDb("C:/Users/empage/Documents/Lab_Stuff/Lab_RNAseq_Tutorial/gencode.v19.annotation.gtf_withproteinids.TxDb")
#k <- keys(txdb, keytype = "TXNAME")
#tx2gene <- select(txdb, k, "GENEID", "TXNAME")
#write.csv(tx2gene, "~/RNAseq_Anoikis/OV90/RNAseq/15U/tx2gene_gencode.v19.annotation.gtf_withproteinids.csv")
```

Option 2: read it in with csv made previously (this will work so long as the txdb is the same)
```{r}
tx2gene <- read.csv("~/RNAseq_Anoikis/OV90/RNAseq/15U/tx2gene_gencode.v19.annotation.gtf_withproteinids.csv")
tx2gene <- tx2gene[ , -1]
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
dir <- "C:/Users/empage/Documents/Lab_Stuff/Anoikis/OV90/treatment_15U/quants"  #this is a path that you will change. This is the quants folder from Salmon that should be locally on your computer 
samples <- read.csv(file= "C:/Users/empage/Documents/Lab_Stuff/Anoikis/OV90/treatment_15U/meta_15U_updated.csv") 
files <- file.path(dir, samples$Sample_ID, "quant.sf")
all(file.exists(files))
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
txi <- tximport(files, type = "salmon", tx2gene= tx2gene, ignoreAfterBar= TRUE)
names(txi)
```

This is for setting up the meta data and DESeq2 object so that you can do your analysis 
```{r message= FALSE, warning= FALSE, echo=FALSE}
sample_meta_data <- read.csv(file= "C:/Users/empage/Documents/Lab_Stuff/Anoikis/OV90/treatment_15U/meta_15U_updated.csv") 
sampleFiles <- samples$Sample_ID
sampleCondition <- sample_meta_data$Passage_ID
sampleTable <- data.frame(sampleName = sampleFiles,
                          fileName = sampleFiles,
                          condition = sampleCondition)
sampleTable$condition <- factor(sampleTable$condition)
```


```{r echo=FALSE}
colnames(txi$counts) <- rownames(sampleTable)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- DESeqDataSetFromTximport(txi, sampleTable, ~condition)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- DESeq(dds)
```

```{r}
counts <- counts(dds[ , ], normalized = FALSE)
write.csv(counts, "~/RNAseq_Anoikis/OV90/RNAseq/15U/raw_counts_15U.csv")
```

```{r}
counts <- counts(dds[ , ], normalized = TRUE)
write.csv(counts, "~/RNAseq_Anoikis/OV90/RNAseq/15U/counts_15U.csv")
```

  
This is going to tell you information about the results from running DESeq2 
```{r}
res <- results(dds, contrast= c("condition", "P1_15U","P0_15U"))
summary(res)
```

```{r echo=FALSE}
plotMA(res, ylim=c(-2,2))
```
You can set results to whatever you want to compare from the dds object; see documentation for more if you do not like what it auto selects/ you want more than what this did first 
Here is an example template. There's a # in front of it so that it is not running 
```{r}
res_2 <- results(dds, contrast=c("condition","P1.1_15U", "P0_15U"))
summary(res_2)
```

```{r echo=FALSE}
plotMA(res_2, ylim=c(-2,2))
```

```{r}
res_3 <- results(dds, contrast=c("condition","P1_15U","P1.1_15U"))
summary(res_3)
```

```{r echo=FALSE}
plotMA(res_3, ylim=c(-2,2))
```

```{r}
res_4 <- results(dds, contrast=c("condition","P1_DMSO","P1.1_DMSO"))
summary(res_4)
write.csv(res_4, "~/RNAseq_Anoikis/OV90/RNAseq/15U/normalization_both_groups/res/P1_P11_DMSO.csv")
```
```{r echo=FALSE}
plotMA(res_4, ylim=c(-2,2))
```

```{r}
res_5 <- results(dds, contrast=c("condition", "P1.1_DMSO", "P0_DMSO"))
summary(res_5)
write.csv(res_5, "~/RNAseq_Anoikis/OV90/RNAseq/15U/normalization_both_groups/res/P11_P0_DMSO.csv")
```
```{r echo=FALSE}
plotMA(res_5, ylim=c(-2,2))
```

```{r}
res_6 <- results(dds, contrast=c("condition", "P1_DMSO", "P0_DMSO"))
summary(res_6)
write.csv(res_6, "~/RNAseq_Anoikis/OV90/RNAseq/15U/normalization_both_groups/res/P1_P0_DMSO.csv")
```

```{r echo=FALSE}
plotMA(res_6, ylim=c(-2,2))
```

```{r}
res_7 <- results(dds, contrast=c("condition","P0_15U","P0_DMSO"))
summary(res_7)
write.csv(res_7, "~/RNAseq_Anoikis/OV90/RNAseq/15U/normalization_both_groups/res/P0_15U_DMSO.csv")
```

```{r echo=FALSE}
plotMA(res_7, ylim=c(-2,2))
```

```{r}
res_8 <- results(dds, contrast=c("condition","P1_15U","P1_DMSO"))
summary(res_8)
write.csv(res_8, "~/RNAseq_Anoikis/OV90/RNAseq/15U/normalization_both_groups/res/P1_15U_DMSO.csv")
```

```{r echo=FALSE}
plotMA(res_8, ylim=c(-2,2))
```

```{r}
res_9 <- results(dds, contrast=c("condition","P1.1_15U","P1.1_DMSO"))
summary(res_9)
write.csv(res_9, "~/RNAseq_Anoikis/OV90/RNAseq/15U/normalization_both_groups/res/P11_15U_DMSO.csv")
```

```{r echo=FALSE}
plotMA(res_9, ylim=c(-2,2))
```
for the object as a whole  
```{r}
vsd <- vst(dds, blind=FALSE)
```

```{r}
rld <- rlog(dds, blind=FALSE)
```

```{r}
ntd <- normTransform(dds)
```

```{r}
plotPCA(vsd, intgroup=c("condition"))
```

```{r}
plotDispEsts(dds)
```

