---
title: "WXS_OV90"
output: html_document
date: "2023-06-26"
---
```{r}
library(maftools)
library(ggplot2)
```

Goals: 
1. We want to know what is happening at P0 by itself 
2. See the mutational burden at the start point 
3. More in depth to see what is happening

What we are going to do
1. Do the maftools vignette for each time point separately
2. Make figures where each time point has detailed annotations 

Each time point (P0, 1, 4, 7) has 2 files, so each portion will need its own merge step. 
These steps will only be to see what is happening for each time point. No comparisons are being done 

#P0
```{r}
mafs <- c("~/Documents/Mythreye_Lab/Anoikis_Project/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P0_1.mutect2.vep.maf", "~/Documents/Mythreye_Lab/Anoikis_Project/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P0_2.mutect2.vep.maf")
anoikis_maf_P0 <- merge_mafs(mafs)
```

```{r}
#Shows sample summary.
save_mutation_type <- getSampleSummary(anoikis_maf_P0)
write.csv(save_mutation_type, "~/Desktop/wxs_anoikis_ov90_mutations_P0.csv")
```

```{r}
#Shows gene summary.
summary_gene <- getGeneSummary(anoikis_maf_P0)
write.csv(summary_gene, "~/Desktop/wxs_anoikis_ov90_mutations_by_gene_P0.csv")
```

```{r}
#shows clinical data associated with samples
getClinicalData(anoikis_maf_P0)
```

```{r}
#Writes maf summary to an output file with basename laml.
write.mafSummary(maf = anoikis_maf_P0, basename = 'anoikis_maf')
```

```{r}
plotmafSummary(maf = anoikis_maf_P0, rmOutlier = TRUE, addStat = 'median', dashboard = TRUE, titvRaw = FALSE)
```

```{r}
oncoplot(maf = anoikis_maf_P0, top = 10)
```

```{r}
laml.titv = titv(maf = anoikis_maf_P0, plot = FALSE, useSyn = TRUE)
#plot titv summary
plotTiTv(res = laml.titv)
```

```{r}
rainfallPlot(maf = anoikis_maf_P0, detectChangePoints = TRUE, pointSize = 0.4)
```

```{r, warning= FALSE, message= FALSE, include = FALSE}
laml.sig = oncodrive(maf = anoikis_maf_P0, AACol = 'HGVSp_Short', minMut = 5, pvalMethod = 'zscore')
```

```{r}
x <- plotOncodrive(res = laml.sig, fdrCutOff = 0.1, useFraction = TRUE, labelSize = 0.5)
x + scale_x_continuous(limits = c(0.0 , 1.5))
```

#P1
```{r}
mafs <- c("~/Documents/Mythreye_Lab/Anoikis_Project/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P1_1.mutect2.vep.maf", "~/Documents/Mythreye_Lab/Anoikis_Project/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P1_2.mutect2.vep.maf")
anoikis_maf <- merge_mafs(mafs)
```

```{r}
#Shows sample summary.
save_mutation_type <- getSampleSummary(anoikis_maf)
write.csv(save_mutation_type, "~/Desktop/wxs_anoikis_ov90_mutations_P1.csv")
```

```{r}
#Shows gene summary.
summary_gene <- getGeneSummary(anoikis_maf)
write.csv(summary_gene, "~/Desktop/wxs_anoikis_ov90_mutations_by_gene_P1.csv")
```

```{r}
#shows clinical data associated with samples
getClinicalData(anoikis_maf)
```

```{r}
#Writes maf summary to an output file with basename laml.
write.mafSummary(maf = anoikis_maf, basename = 'anoikis_maf')
```

```{r}
plotmafSummary(maf = anoikis_maf, rmOutlier = TRUE, addStat = 'median', dashboard = TRUE, titvRaw = FALSE)
```

```{r}
oncoplot(maf = anoikis_maf, top = 10)
```

```{r}
laml.titv = titv(maf = anoikis_maf, plot = FALSE, useSyn = TRUE)
#plot titv summary
plotTiTv(res = laml.titv)
```

```{r}
rainfallPlot(maf = anoikis_maf, detectChangePoints = TRUE, pointSize = 0.4)
```

```{r, warning= FALSE, message= FALSE, include = FALSE}
laml.sig = oncodrive(maf = anoikis_maf, AACol = 'HGVSp_Short', minMut = 5, pvalMethod = 'zscore')
```

```{r}
plotOncodrive(res = laml.sig, fdrCutOff = 0.1, useFraction = TRUE, labelSize = 0.5) + scale_x_continuous(limits= c(0, 1.5))
```

#P4
```{r}
mafs <- c("~/Documents/Mythreye_Lab/Anoikis_Project/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P4_1.mutect2.vep.maf", "~/Documents/Mythreye_Lab/Anoikis_Project/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P4_2.mutect2.vep.maf")
anoikis_maf <- merge_mafs(mafs)
```

```{r}
#Shows sample summary.
save_mutation_type <- getSampleSummary(anoikis_maf)
write.csv(save_mutation_type, "~/Desktop/wxs_anoikis_ov90_mutations_P4.csv")
```

```{r}
#Shows gene summary.
summary_gene <- getGeneSummary(anoikis_maf)
write.csv(summary_gene, "~/Desktop/wxs_anoikis_ov90_mutations_by_gene_P4.csv")
```

```{r}
#shows clinical data associated with samples
getClinicalData(anoikis_maf)
```

```{r}
#Writes maf summary to an output file with basename laml.
write.mafSummary(maf = anoikis_maf, basename = 'anoikis_maf')
```

```{r}
plotmafSummary(maf = anoikis_maf, rmOutlier = TRUE, addStat = 'median', dashboard = TRUE, titvRaw = FALSE)
```

```{r}
oncoplot(maf = anoikis_maf, top = 10)
```

```{r}
laml.titv = titv(maf = anoikis_maf, plot = FALSE, useSyn = TRUE)
#plot titv summary
plotTiTv(res = laml.titv)
```

```{r}
rainfallPlot(maf = anoikis_maf, detectChangePoints = TRUE, pointSize = 0.4)
```

```{r, warning= FALSE, message= FALSE, include = FALSE}
laml.sig = oncodrive(maf = anoikis_maf, AACol = 'HGVSp_Short', minMut = 5, pvalMethod = 'zscore')
```

```{r}
plotOncodrive(res = laml.sig, fdrCutOff = 0.1, useFraction = TRUE, labelSize = 0.5) + scale_x_continuous(limits= c(0, 1.5))
```

#P7
```{r}
mafs <- c("~/Documents/Mythreye_Lab/Anoikis_Project/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P7_1.mutect2.vep.maf", "~/Documents/Mythreye_Lab/Anoikis_Project/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P7_2.mutect2.vep.maf")
anoikis_maf_P7 <- merge_mafs(mafs)
```

```{r}
#Shows sample summary.
save_mutation_type <- getSampleSummary(anoikis_maf_P7)
write.csv(save_mutation_type, "~/Desktop/wxs_anoikis_ov90_mutations_P7.csv")
```

```{r}
#Shows gene summary.
summary_gene <- getGeneSummary(anoikis_maf_P7)
write.csv(summary_gene, "~/Desktop/wxs_anoikis_ov90_mutations_by_gene_P7.csv")
```

```{r}
#shows clinical data associated with samples
getClinicalData(anoikis_maf_P7)
```

```{r}
#Writes maf summary to an output file with basename laml.
write.mafSummary(maf = anoikis_maf_P7, basename = 'anoikis_maf')
```

```{r}
plotmafSummary(maf = anoikis_maf_P7, rmOutlier = TRUE, addStat = 'median', dashboard = TRUE, titvRaw = FALSE)
```

```{r}
oncoplot(maf = anoikis_maf_P7, top = 10)
```

```{r}
laml.titv = titv(maf = anoikis_maf_P7, plot = FALSE, useSyn = TRUE)
#plot titv summary
plotTiTv(res = laml.titv)
```

```{r}
rainfallPlot(maf = anoikis_maf_P7, detectChangePoints = TRUE, pointSize = 0.4)
```

```{r, warning= FALSE, include = FALSE}
laml.sig = oncodrive(maf = anoikis_maf_P7, AACol = 'HGVSp_Short', minMut = 5, pvalMethod = 'zscore')
```

```{r}
x <- ggplot(plotOncodrive(res = laml.sig, fdrCutOff = 0.1, useFraction = TRUE, labelSize = 0.5)) + geom_point() 
```

```{r}
x <- mafCompare(anoikis_maf_P0, anoikis_maf_P7, m1Name="P0", m2Name="P7", minMut= 0)
```

```{r}
write.csv(x[["results"]], "~/Desktop/maf_P0_P7_WXS_comparisons.csv")
```


```{r}
mafs <- c("~/Documents/Mythreye_Lab/anoikis/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P0_1.mutect2.vep.maf", "~/Documents/Mythreye_Lab/anoikis/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P0_2.mutect2.vep.maf", "~/Documents/Mythreye_Lab/anoikis/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P7_1.mutect2.vep.maf", "~/Documents/Mythreye_Lab/anoikis/Mehri_Resha/anoikis/ovarian_cancer_somatic_variants_mafs/WXS/P7_2.mutect2.vep.maf")
merged_P0_P7 <- merge_mafs(mafs)
```
```{r}
#shows clinical data associated with samples
getClinicalData(merged_P0_P7)
```

```{r}
#Writes maf summary to an output file with basename laml.
write.mafSummary(maf = merged_P0_P7, basename = 'anoikis_maf')
```

```{r}
summary_gene$Hugo_Symbol -> gene_list
genes <- c("MUC6", "MUC3A", "MUC4", "LILRB1", "HLA-B", "HLA-DRB5", "KIR2DL4", "LILRB2", "MUC12", "MUC16", "LILRA1", "HLA-DRB1",  "HRNR", "LILRA2", "TAS2R31", "TAS2R46", "OR8U1", "KIR2DL1", "PRSS1", "HLA-DQB1", "HLA-A", "HLA-C", "IGHV1-2", "OR9G1")
genes2 <- c("TRBV3-1", "KIR3DL2", "KIR2DL3", "LILRA4", "ERVW-1", "TUBB8B", "CNN2", "HLA-DQA1", "FCGBP", "GSTT4", "IGLV5-45", "SIRPA", "GOLGA6L2", "PRSS3", "TAS2R19", "IGHV1-69", "ZNF717", "AHNAK2", "IGLV5-48", "MUC20", "SLC25A5", "TAS2R43", "FAM90A23P", "GOLGA6L10", "IGHV3-20")
genes3 <- c("IGHV3-43", "IGHV4-61", "PABPC3", "PRAMEF18", "HLA-DQA2", "IGHV1-46", "ANKRD36C", "GPRIN2", "IGHV4-31", "RT18", "MICA", "PSPH", "HLA-DPB1", "HLA-DQB2", "HTT", "KRTAP4-11", "LILRA6", "NBPF1", "PABPC1", "GBP4", "LRRC37A3", "OR10G2", "PRAMEF5", "TAS2R30", "KIR3DL1")
genes4 <- c("CAP1", "CYP2D6", "FRG2C", "IGHV3-48", "IGHV4-59", "KCNJ12", "LILRB3", "MTCH2", "RIMBP3", "TNXB", "AGAP4", "ANKRD36", "PLIN4", "C1orf87", "CRYBG2", "DNAH14", "FAM186A", "FMN2", "GOLGA6L6", "IGHV2-5", "IGHV3-21", "KIR2DS4", "NPIPB11", "OR2T2", "PCDHA4", "PCLO")
```


#oncoplot for top ten mutated genes.
```{r}
oncoplot(maf = merged_P0_P7 , top = 20)
```

```{r}
pdf("~/Desktop/oncoplot_Ov90_1.pdf",width=11, height=8)
coOncoplot(m1 = anoikis_maf_P0, m2 = anoikis_maf_P7, m1Name = 'P0', m2Name = 'P7', genes= genes, removeNonMutated = TRUE)
dev.off()
```

```{r}
pdf("~/Desktop/oncoplot_Ov90_2.pdf",width=11, height=8)
coOncoplot(m1 = anoikis_maf_P0, m2 = anoikis_maf_P7, m1Name = 'P0', m2Name = 'P7', genes= genes2, removeNonMutated = TRUE)
dev.off()
```

```{r}
pdf("~/Desktop/oncoplot_Ov90_3.pdf",width=11, height=8)
coOncoplot(m1 = anoikis_maf_P0, m2 = anoikis_maf_P7, m1Name = 'P0', m2Name = 'P7', genes= genes3, removeNonMutated = TRUE)
dev.off()
```

```{r}
pdf("~/Desktop/oncoplot_Ov90_4.pdf",width=11, height=8)
coOncoplot(m1 = anoikis_maf_P0, m2 = anoikis_maf_P7, m1Name = 'P0', m2Name = 'P7', genes= genes4, removeNonMutated = TRUE)
dev.off()
```
